Component-Based mruby Platform for IoT Devices

### 2017-11-15 ipsj/paper.tex
Add Conclusion

>>>>

This paper presented an extended framework of mruby on TECS, including TINET+TECS and TLSF+TECS.
In the proposed framework, mruby programs can call TINET+TECS functions through the mruby-TECS brigde.
Development of software for IoT devices such as sensors and actuators will be more efficient due to the high productivity of mruby.
TINET+TECS is a componentized version of TINET, a compact TCP/IP protocol stack that uses TECS.
It improves on TINET's configurability while suppressing the overhead of componentization.
Scalability is also improved because the component-based framework simplifies to add/remove and change protocols such as TCP/UDP, IPv4/IPv6, and Ethernet/PPP.
This paper also presented the dynamic connection, a new TECS method, to enable dynamic processing while reducing memory consumption.
TINET+TECS utilizes the dynamic connection to satisfy the TINET specification for supporting the static generation of CEPs and REPs.
TLSF+TECS is a component-based dynamic allocator.
Since the TLSF+TECS can hold own heap area, memory contention will not occur even if memory is simultaneously allocated or released from multiple threads.
The heap size can be easily changed because it is set as a variable of the component.
In addition, the RiteVMs, TLSF+TECS, TLSF+TECS are implemented as components; therefore, developers can add, remove, or reuse their functionalities easily as required.
Note that our prototype system and the application programs used in the performance evaluation are all open-source and can be downloaded from our website \cite{url:TECS}.
In the future, we will support mruby libraries as mrbgems, which is an mruby distribution packaging system.\newline
